\documentclass{resume}

\begin{document}

% Name
\name{Utsav Deep}

% Contact Info
\contactsection{\address{Bangalore, India}}{\email{utsavdeep022@outlook.com}}{\phone{+91 - 8088013139}}{\github{https://github.com/pinnheads}}{\linkedin{https://www.linkedin.com/in/utsavdeep}}{\website{https://utsavdeep.com}}

% Sumnmary
\section{Summary}
\begin{summary}
  Test Associate with over 2.5 years of experience specializing in automation testing. Proficient in a variety of modern automation tools and programming languages including JAVA, Selenium, Cucumber, Appium, and other test automation tools. Demonstrated ability to design and improve test automation frameworks and drive efficient, reliable results. Committed to maintaining cutting-edge technical skills and up-to-date industry knowledge.
\end{summary}

\section{Work Experience}
\resumeSubHeadingListStart
  \datedsubsection
    {Test Associate}{January 2022 - Current}
    {Intact Green Services (IGS)}{Bangalore, India}
  \resumeItemListStart
    \resumeItem{Utilized \textbf{SerenityBDD, Selenium, RestAssured, Cucumber} framework with Java to automate over 40 End-to-End tests along with integration and functional testing}
    \resumeItem{Implemented NodeJS based server routes to interact with \textbf{CloudWatch Logs} to verify backend functionality and automate component level tests}
    \resumeItem{Established a robust \textbf{mobile device testing automation} framework using \textbf{Appium}, contributing to the enhancement of testing efficiency and effectiveness.}
    \resumeItem{Played a key role in the proof-of-concept for two online payment applications by creating and executing API tests using \textbf{TestNG and RestAssured}}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \datedsubsection
  {Trainee Consultan}{July 2021 - December 2021}
  {Intact Green Services (IGS)}{Bangalore, India}
  \resumeItemListStart
  \resumeItem{Automated over 300 \textbf{regression tests} using the Selenium/WebDriver framework, significantly reducing the time needed for regression test execution}
  \resumeItem{Set up a proof-of-concept \textbf{CI pipeline} with \textbf{Jenkins and GitHub} for automatic test execution and email alerts for better \textbf{observability}.}
  \resumeItem{\textbf{Trained} manual testers on WebDriverIO and SerenityBDD, promoting a \textbf{team-wide approach} to test automation.}
  \resumeItem{Collaborated with manual testers for \textbf{functional testing} by creating and running functional tests and logging defects using Jira, Testrail, and Browserstack.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \datedsubsection
    {Intern}{June 2019 - August 2019}
    {Cushy.com}{Bangalore, India}
  \resumeItemListStart
    \resumeItem{Collaborated with the marketing team to \textbf{gather potential customer data} from platforms like Google and Zomato, enhancing our customer outreach.}
    \resumeItem{Gained insights into \textbf{client and team management} by shadowing the Marketing team leader, which included learning the art of making effective cold calls.}
    \resumeItem{Conducted cold calls to pitch sales to potential customers, successfully onboarding them onto our app.}
    \resumeItem{Undertook field visits to local businesses for onboarding and \textbf{provided demos} of our application, demonstrating its potential to aid their growth.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
% Education detail
\section{Education}
\resumeSubHeadingListStart
  \datedsubsection
    {Presidency University}{Bangalore, Karnataka, India}
    {Bachelors of Technology in Computer Science and Engineering}{Aug. 2017 -- May. 2021}
\resumeSubHeadingListEnd
\end{document}